---
output:
  word_document: default
  html_document: default
---
author: "ejakait" date: "8-9-2025" output: word_document: number_sections: true editor_options: markdown: wrap: 72

#bibliography: Senegal_SCH.bib #link-citations: true


Signs (Comparison Operators)
These are like questions you ask your data and R answers TRUE or FALSE
Sign	Meaning	Example	Result
==	Equals to	5 == 5	TRUE
!=	Not equal to	5 != 3	TRUE
>	Greater than	7 > 2	TRUE
<	Less than	4 < 6	TRUE
>=	Greater than or equal to	5 >= 5	TRUE
<=	Less than or equal to	3 <= 3	TRUE

#create a vector of ages of students

```{r}
age <- c(15, 20, 25)
```

Who is older than 18?
 
```{r}
age > 18
```
```{r}
# Who is younger than 30?
age < 30 
```

Operators
These are used to combine questions, like asking more than one question at once
Sign	Meaning	Example	Result
&	AND - Both conditions must be TRUE	(5 > 3) & (2 < 4)	TRUE
|	OR - At least one condition must be TRUE	
(5>10)|(2<4)


3. if

```{r}
a <- 30
b <- 20

if (b > a) {
  print("b is greater than a")
}
```



4. else if - you are telling R that if the previous conditions 
were not true, then try this other condition

```{r}
a <- 30
b <- 30

if (b > a){
  print("b is greater than a")
} else if (a == b){
  print("b is equal to a")
}
```

