---
title: "Pre-class exercise"
author: "Ejakait Vincent"
date: "2025-08-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

1.	What is the result of running this code in R?
x <- "hello"
y <- 1
z <- c(x, y)

```{r Q.1}
x <- "hello"
y <- 1
z <- c(x, y)
```

Creates objects x = "hello", y = 1, z = combination of "hello" and "1"


•	What is the data type of x and y
```{r}
typeof(x)
typeof(y)
```
2.	Try this in R and say the output
typeof(TRUE)
typeof(3.14)
typeof("R is fun")
typeof(c(1, 2, 3))

```{r}
typeof(TRUE)
typeof(3.14)
typeof("R is fun")
typeof(c(1, 2, 3))
```

•	Can a vector contain both numbers and characters?
Answer: No, it has to be items of the same type


3.	What does the mean() function do? Try this
mean(c(5, 10, 15))

```{r mean}
mean(c(5, 10, 15))
```
This adds the values inside the concatination and then does the mean (30/3) = 10

•	What happens if you run the following instead?
mean(5, 10, 15)

```{r}
mean(5, 10, 15)
```
This just takes the mean of the firs number "5" (5/1) = 5


4.	R comes with datasets you can explore. Try running this and explain what kind of data you see:
data()
head(mtcars)

```{r}
data()
head(mtcars)
```

5.	Find out what function is used to import a .csv file and an .xlsx file into R.
ANS:  read_csv() is used to import .csv file
      read_xlsx() is used to import .xlsx
      
      

6.	Find out the difference between c(), list(), and data.frame()
c() can carry data of different types 
list() houses only data of the same type
data.frame() occurs as a two dimensional table


creating factors
```{r}
df_1 <- factor(c("male", "female"))
df_2 <-  c("male", "female")
typeof(df_2)
df_3 <- as.factor(df_2)
typeof(df_3)
class(df_3)
```

create levels for factor data

```{r}
levels(df_3)
edu_level <- factor(c(1, 2, 3), levels = c("primary", "secondary", "tertiary"))
class(edu_level)
levels(edu_level)
```


